\chapter{Introduction}\label{ch:introduction}

The case chosen for this assignment was project 3 regarding simulator for wireless communication. Based on the assignment description, the report will contain information about all the phases of the project; Analysis, Design, how the design was implemented, major decisions that we needed to take and finally the live product.\newline

The wireless network simulator involved designing a software that simulates wireless communication between nodes. Furthermore, the nodes are to be places in different position in a user defined space and they are to communicate with each other. In the assignment description, the program is required to have these additional aspects:
\begin{itemize}
    \item User must choose different type of nodes such as base stations, mobile phones, drones, satellites...
    \item A subset of nodes may transmit a block of data selecting a certain power, frequency, bandwidth and time of transmission
    \item A subset of nodes may listen to incoming data and try to decode the data
    \item A GUI is used to insert and remove nodes. It is also used to start and stop data communication and to show communication quality information of each node 
\end{itemize}

We then proceeded to carry on with the first stage of the waterfall model which is Analysis. During the Analysis, we discovered additional considerations that we would need to take into account. This resulted in the group coming up with a use-case diagram and a class diagram. Then the simulator was implemented in python. During this project, the group had encountered some challenges which would be discussed in the report.







